% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\LARGE \bf Bridger Hahn}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{\large bridgerhahn@gmail.com}
 \moveleft.5\hoffset\centerline{\large http://github.com/bridgar}
 \moveleft.5\hoffset\centerline{\large (440) 417-8328}


\begin{resume}

\section{}
\section{}


\section{OBJECTIVE} I am interested in a software engineering internship for the Summer of 2015. I have had firm experience with web development and theoretical computer science; I would like to try software development, particularly game development.
 

\section{EDUCATION} {\sl Bachelor of Science} \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                Stony Brook University, Stony Brook, NY, 
                expected June 2016 \\
                Majors: Computer Science and Applied Math \\
                Transcript available upon request \\
                Cum GPA 3.36

\section{AWARDS \& ACCOMPLISHMENTS}
                Stony Brook University Honors College Member \\
                Computer Science Honors Member \\
                Dean's List Fall 2012 - Spring 2014 \\
                Stony Brook Provost's Scholarship awarded upon acceptance
 
 
\section{LANGUAGES} Proficiency in Java, SQL, C\#, C++\\
Capable with JavaScript, PHP, HTML and CSS \\

\section{IMPORTANT COURSES TAKEN}
\begin{tabular}{c c c}
Algorithms & Databases & Systems Programming \\
&&\\
Computer Architecture & 2D and 3D Game Development & Computational Geometry\\
\end{tabular}
               

 
\section{EXPERIENCE} 
                {\sl Research} \hfill           Summer 2014-Present \\
                Professor Bender, Stony Brook University
                \begin{itemize} \itemsep -2pt
                \item Working on various problems, searching for one that will result in a paper.
                \item ex. Maximum Prefix Overlap
                \item ex. Reallocation
                \end{itemize}
                {\sl Web Developer} \hfill    Spring 2014-Present \\
                Division of Information Technologies, Stony Brook University
                \begin{itemize} \itemsep -2pt
                \item Maintain and currently working on redesigning it.stonybrook.edu.
                \item Built classie.stonybrook.edu and classie-evals.stonybrook.edu from scratch in drupal and .NET respectively. Currently preparing both for late 2014 launch.
                \item Classie.stonybrook.edu is a syllabus database. It acts as a front-end for syllabus submission from professors and a JSON feed for class search and scheduling sites.
                \item Classie-evals.stonybrook.edu is a student evaluation database. It houses quantitative and qualitative student responses about courses and instructors. It sits behind CAS authentication, thus can still be freely linked to from class search and scheduling sites.
\\
\\
                \end{itemize}
                {\sl Research} \hfill           Fall 2013 \\
                Professor Scarlatos, Stony Brook University
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Worked on a prototype for language-learning software for second-generation Americans.
                 \item After prototype had been developed and reviewed, it was decided that the market was saturated. I learned critical project planning and execution skills.
                 \end{itemize} 

\section{EXTRA-CURRICULAR \\ ACTIVITIES}             
            Elected {\it Treasurer}, Stony Brook Computing Society (Fall 2013) \\
            Hacked at MHacks 2013 \\
            Member of the Association for Computing Machinery
 
\section{LEADERSHIP}

            Treasurer of the Stony Brook Computing Society (2013-2014)\\
            Member of the National Honor Society \\
            Presented four experiments for ACS National Chemistry Week (2011) \\
            Three years of Big Brothers and Big Sisters (2008-2011)

\end{resume}
\end{document}




